Investigating magnetic dynamo evolution with \TESS\ field dwarfs

### 2017-10-06 ms.tex
edits

\citet{oh2016} identified over 10,000 comoving pairs of stars using proper
motions from the first \Gaia\ data release.
Of these, 8 dwarfs and subgiants in 4 pairs have \RAVE\ radial velocities
consistent with being comoving and are already in the Candidate Target List.
Following \citet{campante2016} we calculate that these stars have oscillation
detection probabilities greater than 0.85, based on their \RAVE-on
T$_{\mathrm{eff}}$, $\log g$ and radii \citep{casey2017} and their observation
baseline, from {\tt tvguide}.
Since these stars would make interesting targets for both asteroseismology and
exoplanet search, we include a list with this proposal.
The stars in these pairs are likely recently disrupted binaries so we
expect them to have similar ages and measuring their rotation periods will
therefore provide a test of gyrochronology.
An additional 5000 bright comoving pair candidates lie in the southern
ecliptic hemisphere and will be ideal FFI targets for gyrochronology studies.
{\bf We will use the rotation periods of comoving stars to quantify the
accuracy and precision of gyrochronology.}

>>>>

\citet{oh2016} identified over 10,000 comoving pairs of stars using proper
motions from the first \Gaia\ data release.
Of these, 8 dwarfs and subgiants in 4 pairs have \RAVE\ radial velocities
consistent with being comoving and are already in the Candidate Target List.
Following \citet{campante2016} we calculate that these stars have oscillation
detection probabilities greater than 0.85, based on their \RAVE-on
T$_{\mathrm{eff}}$, $\log g$ and radii \citep{casey2017} and their {\tt
tvguide} \citep{tvguide} observation baseline.
Since these stars would make interesting targets for both asteroseismology and
exoplanet search, we include a list with this proposal.
The stars in these pairs are likely recently disrupted binaries so we expect
them to have similar ages and measuring their rotation periods
will therefore provide a test of gyrochronology, even in cases where
asteroseismic ages are unavailable.
An additional 5000 bright comoving pair candidates lie in the southern
ecliptic hemisphere and will be ideal FFI targets for gyrochronology studies.
{\bf We will use the rotation periods of comoving stars to quantify the
accuracy and precision of gyrochronology.}
